% Compiles on Overleaf default pdfLaTeX and Xe/LuaLaTeX.
\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.0cm]{geometry}
\usepackage{xcolor}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{newpxtext}
\else
  \usepackage{fontspec}
  \setmainfont{TeX Gyre Pagella}
\fi
\usepackage{fancyhdr}
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\usepackage{fvextra}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{tikz}
\usepackage{setspace}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textit{Green V2X Project Overview Dossier}}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\emergencystretch}{3em}
\setstretch{1.03}
\titleformat{\section}{\Large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\large\bfseries}{}{0pt}{}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black
}
\fvset{
  breaklines=true,
  breakanywhere=true,
  fontsize=\footnotesize,
  baselinestretch=0.93
}

\definecolor{UserBG}{HTML}{F4F8FF}
\definecolor{AsstBG}{HTML}{F6FBF7}
\definecolor{UserBorder}{HTML}{335C99}
\definecolor{AsstBorder}{HTML}{2E7D5B}
\definecolor{TitleColor}{HTML}{102A43}
\definecolor{SubtitleColor}{HTML}{486581}

\newenvironment{userbox}
  {\begin{tcolorbox}[
    breakable,
    colback=UserBG,
    colframe=UserBorder,
    title=Source Request Extract,
    fonttitle=\bfseries\small\color{white},
    coltitle=white,
    colbacktitle=UserBorder,
    boxrule=0.5pt,
    arc=1.2mm,
    left=1.4mm,right=1.4mm,top=0.8mm,bottom=0.8mm,
    boxsep=0.6mm,
    before skip=0pt,
    after skip=0pt
  ]}
  {\end{tcolorbox}}

\newenvironment{assistantbox}
  {\begin{tcolorbox}[
    breakable,
    colback=AsstBG,
    colframe=AsstBorder,
    title=Project Overview Extract,
    fonttitle=\bfseries\small\color{white},
    coltitle=white,
    colbacktitle=AsstBorder,
    boxrule=0.5pt,
    arc=1.2mm,
    left=1.4mm,right=1.4mm,top=0.8mm,bottom=0.8mm,
    boxsep=0.6mm,
    before skip=0pt,
    after skip=0pt
  ]}
  {\end{tcolorbox}}

\begin{document}

\begin{center}
\begin{tikzpicture}
\fill[TitleColor] (0,0) rectangle (13.4,1.4);
\node[anchor=west,text=white,font=\bfseries\Large] at (0.35,0.92) {Green V2X \_Energy Aware Handoff};
\node[anchor=west,text=white,font=\bfseries\large] at (0.35,0.42) {Comprehensive Project Overview Dossier};
\end{tikzpicture}\\[6pt]
{\normalsize\color{SubtitleColor} Full transcript content preserved verbatim (no text alteration)}\\[2pt]
{\small\color{SubtitleColor} Presentation transformed from chat layout to overview-style archival report}
\end{center}
\vspace{10pt}

\begin{userbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
FIrst checkout the whole project.

Then tell me what is this project about ?

what is the algorithm here ?

How everything works ?

and also what goal/result is achieving this project ?

I need simple but detailed explanation in easy words please
\end{Verbatim}
\end{userbox}

\begin{assistantbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Here’s a concise picture of the project after reading the main docs and core code (no `git checkout` was needed—you meant “look over” the repo).

## What this project is about

**Green V2X** is a **computer simulation** of cars on a **highway** talking to **cell towers (base stations)** over the **uplink** (vehicle -> tower). In real life, a car must **choose which tower to use** as it moves; that choice is called **handoff**.

This repo implements **several handoff rules**, especially one that tries to **save radio energy** (and then **CO2**, using grid electricity intensity). It is **not** a live network stack—it’s a **research-style discrete-time simulator** that steps time, moves vehicles, updates radio, counts handoffs, and totals energy and throughput.

## What the main algorithm is (energy-aware handoff)

The **star algorithm** is **`EnergyAwareHandoff`** in `src/algorithms/energy_aware_handoff.py`. In plain terms it does this:

1. **For each candidate tower**, it estimates:
   - **Transmit power** needed for a reliable link (path loss, weather, shadowing).
   - **Data rate** from a Shannon-style formula using **SINR** (signal vs noise + interference).
   - **Energy per bit (EPB)** = how many joules of device power you spend per bit sent, using the **energy model** (PA, circuits, baseband, etc.).
2. It **combines EPB with tower load**: a tower with more users gets a **worse score** (higher “metric”), so the policy prefers **less loaded** cells when EPB is similar—**load balancing**.
3. It applies **QoS filters** (minimum data rate, minimum SINR) so it doesn’t pick “cheap but useless” links.
4. **Cell-edge penalty**: if you’re far from the tower (near the edge), the **metric is worse**, so it prefers **more central / stable** connections when possible.
5. **When to actually hand off** (`should_handoff`) uses:
   - **Escape** if the current tower is **overloaded**.
   - **Urgent** switch if **SINR is bad** or **EPB is too high** (bad link).
   - Otherwise: **hysteresis**—only switch if the new tower is **meaningfully better** in energy terms (not tiny gains).
   - **Don’t** switch to a clearly **worse SINR** link.
   - **Time-to-trigger (TTT)** and **cooldowns** so cars don’t **ping-pong** between towers.

**Baselines** (for comparison): strongest **RSSI**, **SINR**-based, **load-aware RSSI**, and **nearest tower** geographically. These are classic or simple rules; the energy-aware one is the one that **explicitly optimizes EPB + load + stability**.

## How everything works (end-to-end)

1. **`SimulationConfig`** (`simulations/config.py`) sets the world: area size, number of towers, vehicles, speeds, **highway lanes**, **weather profile**, **carbon intensity** (kg CO2 per kWh), duration, time step, etc.
2. **`V2XSimulator`** (`simulations/simulator.py`):
   - Places **base stations** on a **grid**.
   - Spawns **vehicles** (highway mode: fixed lane centers, lane speeds, optional lane changes).
   - Each **time step**: vehicles move, **shadowing/SINR/interference** are computed (cached per step for fairness), each algorithm decides **stay or hand off**.
   - **Energy** accumulates from **transmit power × time**, **handoff overhead** (extra energy and delay), **bits sent**, etc.
   - `run_comparison()` runs **each algorithm** with a **fresh reset** of vehicle and BS state so results are fair.
3. **`main.py`** runs **multi-seed** experiments, **paired t-tests** (e.g. RSSI vs energy-aware), **plots**, **scaling** (more vehicles), **energy-parameter sensitivity**, **scenario diversity** (weather / urban), and optional **Bangladesh grid** CO2 numbers.

So: **config -> build map -> simulate time -> policies differ -> metrics compared**.

## Goal and what result it achieves

**Goal:** Show that **handoff can be chosen to reduce uplink energy** (and **CO2**) compared to usual signals-only rules, **without** necessarily giving up throughput, and ideally with **fewer unnecessary handoffs** or **better stability** in some cases.

**Typical outputs** (under `results/`, described in the README):

- **Energy saving %** (energy-aware vs RSSI and others), **energy per bit**, **total joules**.
- **Handoffs**, **ping-pong**, **handoff delay**, **service availability**, **outage** (coverage gaps vs SINR).
- **CO2** estimates from energy × **grid carbon intensity**.
- **Plots** (bars, CDFs, scaling curves, weather sweeps, etc.).

The README also notes a **sanity check**: e.g. **>15% EPB saving vs RSSI** on at least one seed in the paper baseline scenario—this is a **project-specific success criterion**, not a universal law.

## In one sentence:

This project **simulates highway V2X**, compares **how handoff is decided**, and argues that an **energy- and load-aware** policy can **use less transmit energy and associated CO2** than **RSSI/SINR/nearest** baselines, while reporting **full radio and QoS-style statistics**—all in **software**, for **research and reporting** rather than deployment in real cars.
\end{Verbatim}
\end{assistantbox}

\begin{userbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Now check the whole project rigorously and thoroghly.
Deeply understand each and everything of this project.
Then provide me a full detailed summary 
\end{Verbatim}
\end{userbox}

\begin{assistantbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
## Project Deep-Dive Summary

This project is a **research-oriented V2X handoff simulation framework** that compares multiple handoff strategies with a strong focus on **energy efficiency and CO2 reduction**, while still tracking QoS-like behavior (throughput, outage, availability, handoff stability).

## What the project is, in one line

It simulates moving vehicles and cellular base stations over time, runs several handoff algorithms under matched conditions, and reports whether the custom **energy-aware handoff** outperforms standard baselines.

## Repository architecture

- `main.py`: primary experiment orchestrator (baseline, multi-seed stats, t-tests, scaling, sensitivity, scenario diversity, plotting).
- `simulations/config.py`: all simulation/scenario parameters and scenario factory presets.
- `simulations/simulator.py`: core engine (`V2XSimulator`) and per-algorithm execution/comparison logic.
- `src/models/*`: physical/network entities and models (`vehicle`, `basestation`, `channel`, `weather`, `energy`).
- `src/algorithms/*`: 8 handoff algorithms (custom + classical + literature-inspired baselines).
- `src/utils/visualization.py`: plot generation for result analysis.
- `validation_runner.py` + `simulations/validator.py`: extrapolation and hardware/CO2 scope validation.
- `weather_sweep.py`, `sweep_connectivity_energy.py`: robustness/sensitivity sweeps.
- `tests/test_simulation.py`: pytest-based checks (mostly smoke/invariant-level).
- `results/*`: generated outputs (JSON + PNG + markdown notes).

## End-to-end execution flow

- `main.py` loads `SimulationConfig.paper_baseline_scenario()`.
- For each seed in a 15-seed list:
  - create simulator, run `run_comparison()`.
- `run_comparison()`:
  - create BS grid once,
  - for each algorithm: re-seed RNG, regenerate vehicles, run algorithm.
- `run_algorithm()`:
  - time-step loop with movement, candidate selection, handoff decision, energy accounting, outage/availability tracking.
- After seeds:
  - compute mean/std and paired t-tests (`RSSI` vs `energy_aware`),
  - write `results/multiseed_summary.json`,
  - save last-seed full snapshot `results/simulation_results.json`,
  - generate plot set,
  - run scaling/sensitivity/scenario-diversity studies.

## Core simulation model (important mechanics)

- **Mobility**: highway lanes with lane-dependent speeds, stochastic lane switching, wrap-around longitudinal movement.
- **Topology**: BSs on grid; each has coverage radius and capacity.
- **Channel**: path loss + weather attenuation + shadowing + fading + interference.
- **Link rate**: Shannon-style over 20 MHz with outage thresholding.
- **Energy model**: transmit chain power includes PA inefficiency + circuit + baseband + cooling.
- **CO2 model**: converts Joules -> kWh -> kgCO2 via configurable grid intensity, plus optional infrastructure/embodied extensions.

## Handoff algorithms implemented

1. `energy_aware`: EPB + load-aware metric, QoS filtering, SINR guard, hysteresis, cooldown, TTT, forced triggers (overload/low-SINR/high-EPB).
2. `rssi`: strongest received power + RSSI hysteresis.
3. `sinr`: strongest SINR + hysteresis.
4. `load_aware_rssi`: maximize `RSSI - alpha*load`.
5. `naive_nearest`: nearest in-coverage BS (no signal quality intelligence).
6. `literature_ul_ho`: load-gated UL-RSRP + A3 + TTT (Jon et al. baseline).
7. `lb_aware_rsrp`: load-state-aware candidate staging + A3 + TTT (Hatipoglu et al. baseline).
8. `mdpi_energy_efficient`: weighted composite score (RSSI/SINR/BUE/Econs/MUE/QoS) with trigger gates (Abdullah et al. baseline).

## Metric system and what is reported

Per algorithm it reports:
- energy (`total_energy_joules`, `avg_energy_per_bit`),
- traffic (`avg_throughput_bps`, `p5_throughput_bps`),
- reliability (`outage_probability_percent`, `coverage_gap_percent`, `sinr_outage_percent`),
- stability (`total_handoffs`, ping-pong counts/rate, handoff delay),
- service continuity (`avg_service_availability_percent`, p5 availability),
- environmental impact (`co2_kg`, annualized per-vehicle CO2, comprehensive CO2 breakdown).

## Current empirical picture from saved outputs

From `results/multiseed_summary.json`:
- EPB saving (EA vs RSSI): **15.26% ± 1.07%**
- Total energy saving: **9.09% ± 0.55%**
- Handoff reduction: **20.52% ± 0.54%**
- Paired tests highly significant (`p ~ 1e-18`, `1e-17`)

From `results/scaling_results.json`:
- savings stay around **23.15%–23.43%** from 20 to 200 vehicles.

From `results/energy_model_sensitivity.json`:
- savings remain positive across PA efficiency and TX-circuit sweeps (~14–15% range).

From `results/scenario_diversity_results.json`:
- clear: ~17.4%, heavy rain: ~48.8%, urban dense: ~31.4%.

From `results/weather_sweep.json`:
- positive savings across all listed weather profiles, with stronger gains in harsh conditions.

## Validation and testing maturity

- Validation scripts exist for:
  - hardware anchor sanity checks,
  - duration/extrapolation stability,
  - CO2 scope reporting.
- Test suite exists but is concentrated in one file and is mostly:
  - invariant/smoke checks,
  - not deep branch-level verification of algorithm decision logic.
- Strong enough for regression smoke, weaker for formal algorithmic correctness guarantees.

## Important inconsistencies / technical debt found

- **README drift**: some documented baseline values (seed count and certain baseline parameters) do not match current `main.py` / `config.py`.
- **Result interpretation risk**: `simulation_results.json` is last-seed snapshot; multi-seed claims should use `multiseed_summary.json`.
- **Path duplication noise**: Windows `\` and POSIX `/` path variants appear in listings/tool outputs, creating apparent duplicates.
- **Repository hygiene**: generated artifacts and cache files (`__pycache__`, `.pyc`, many result files) are present in working tree.
- **Config validation style**: heavy use of `assert` in config checks (can be bypassed under optimized Python runs).

## Overall assessment

The project is **substantive and technically rich**, with a clear architecture and a credible experiment pipeline.  
Its strongest points are:
- fair seed-controlled comparisons,
- broad metrics (energy + service + environmental),
- multi-scenario robustness analysis,
- publishable artifact generation.

Its weakest points are:
- documentation drift,
- limited depth of automated tests for decision-logic correctness,
- output/repo clutter from generated artifacts.

If you want, next I can produce a **module-by-module annotated map** (every `.py` file with purpose, key classes/functions, and dependencies) as a second, even more exhaustive layer.
\end{Verbatim}
\end{assistantbox}

\begin{userbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Now check out the latest full run of this project. Check all the results the run has created.E every single one. each and every result it created.

Then provide me brief and detailed result of the whole latest full run of this project
\end{Verbatim}
\end{userbox}

\begin{assistantbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
I checked **every unique file currently in `results/`** (JSON, MD, and all PNG plots).  
There are path-separator duplicates (`/` and `\`) in listing output, but they point to the same files.

## Brief result (latest full run)

The latest full `main.py` run is consistent and strong:

- **Multi-seed headline (`multiseed_summary.json`)**
  - EA vs RSSI EPB saving: **15.26% ± 1.07%**
  - EA vs RSSI total-energy saving: **9.09% ± 0.55%**
  - Handoff reduction: **20.52% ± 0.54%**
  - Paired t-tests: very strong significance (`p ≈ 1.5e-18`, `1.65e-17`)

- **Last-seed snapshot (`simulation_results.json`, seed `11235`)**
  - EA beats RSSI on EPB, throughput, outage, and handoff count.
  - MDPI baseline has very low total Joules but **severe service collapse** (very high outage, low throughput).

- **Scalability/sensitivity/diversity outputs** are coherent and positive.
- Weather sweep + validation + parameter sweep artifacts are also present and valid.

---

## Detailed result of the whole latest output set

### 1) Core full-run artifacts (`main.py`)

### `simulation_results.json` (last seed: `11235`, clear weather, 20 vehicles, 16 BS, 1200s)
Key algorithms:

- **Energy-Aware**
  - `total_energy_joules`: **21162.94**
  - `avg_energy_per_bit`: **3.605e-08**
  - `total_handoffs`: **2246**
  - `avg_throughput_bps`: **24.46 Mbps**
  - `outage_probability_percent`: **16.64%**
  - `co2_kg`: **0.002939**

- **RSSI**
  - `total_energy_joules`: **23266.31**
  - `avg_energy_per_bit`: **4.295e-08**
  - `total_handoffs`: **2788**
  - `avg_throughput_bps`: **22.57 Mbps**
  - `outage_probability_percent`: **23.49%**
  - `co2_kg`: **0.003231**

- **Computed from these last-seed values**
  - EPB saving (EA vs RSSI): ~**16.05%**
  - Total-energy saving: ~**9.04%**
  - Handoff reduction: ~**19.44%**
  - Outage reduction: ~**6.85 percentage points**

Other baselines (same file):
- `sinr`: better than RSSI but below EA.
- `load_aware_rssi`: close to RSSI.
- `naive_nearest`: lower total Joules but slightly worse EPB and lower throughput.
- `literature_ul_ho`, `lb_aware_rsrp`: fewer handoffs but weaker EPB/outage.
- `mdpi_energy_efficient`: minimal handoffs/energy but **very poor service** (throughput collapse, outage ~68%).

### `multiseed_summary.json` (15 seeds)
- Confirms EA gains are not seed-specific:
  - EPB: **15.26% mean saving**
  - Total Joules: **9.09% mean saving**
  - Handoffs: **20.52% mean reduction**
  - Statistical significance is very strong.

### 2) Experiment extensions from same full run

### `scaling_results.json` + `scaling_energy_saving_vs_vehicles.png`
- Vehicle counts: 20, 50, 100, 200.
- Savings remain very stable: roughly **23.15%–23.43%**.
- Plot confirms no collapse at high load.

### `energy_model_sensitivity.json` + `energy_model_sensitivity.png` + `energy_model_justification.md`
- PA efficiency sweep (0.25–0.45): mean savings ~**14.43%–15.15%**.
- TX-circuit sweep (0.05–0.15 W): mean savings ~**14.21%–15.17%**.
- Conclusion: EA benefit is robust to reasonable energy-model parameter variation.

### `scenario_diversity_results.json` + `scenario_diversity_energy_saving.png`
- Clear weather: **17.38%**
- Heavy rain: **48.76%**
- Urban dense: **31.35%**
- Claim in file (“positive in all tested scenarios”) is supported.

### 3) Weather robustness outputs (present and valid)

### `weather_sweep.json` + 3 weather PNGs
Means by weather:
- Clear: ~**16.42%** energy saving
- Light rain: ~**20.29%**
- Heavy rain: ~**49.85%**
- Snow: ~**56.87%**
- Fog: ~**29.93%**
- Thunderstorm: ~**69.46%**
- Dust/sand storm: ~**55.49%**
Also includes CI95 for energy/handoff/CO2 savings.

### 4) Validation outputs (present and valid)

### `comprehensive_validation.json` + `extrapolation_validation.png`
- Hardware validation: `validation_passed: true` (OBU in-scope anchor passed).
- Extrapolation study: stable rates across 300–7200s:
  - energy/s CV ~**0.21%**
  - CO2/s CV ~**0.21%**
  - handoffs/s CV ~**0.50%**
- `extrapolation_valid: true`.

### 5) Parameter sweep output (present and parsed)

### `parameter_sweep.json`
- Grid sweep artifact is valid and populated.
- Contains many configurations over coverage radius, TX max power, SINR trigger, EPB limit, hysteresis.
- Observed energy-saving span in file is roughly **~3.23% to ~6.90%** (tradeoff-focused sweep, not the same as core baseline reporting).

### 6) Plot-by-plot check (all visual artifacts verified)

I opened and checked all plot files:
- `bar_co2_comparison.png`
- `bar_comparison.png`
- `energy_comparison.png`
- `cumulative_co2.png`
- `energy_per_vehicle_cdf.png`
- `tx_power_distribution.png`
- `bs_load_distribution.png`
- `sinr_histogram.png`
- `network_topology.png`
- `scaling_energy_saving_vs_vehicles.png`
- `energy_model_sensitivity.png`
- `scenario_diversity_energy_saving.png`
- `weather_sweep_energy_saving.png`
- `weather_sweep_handoff_reduction.png`
- `weather_sweep_co2_saving.png`
- `extrapolation_validation.png`
- `pareto_frontier.png` (present; likely notebook-generated)

---

## Final takeaway

The latest full result set is internally consistent and supports the same conclusion across multiple views:

- **Energy-Aware handoff consistently outperforms RSSI on energy-per-bit and handoff stability**, while generally improving service quality metrics.
- The gains are **multi-seed significant**, **scalable**, and **robust under sensitivity/scenario/weather variations**.
- A few alternative baselines can lower absolute Joules in some snapshots, but often by sacrificing throughput/availability, which the EA method avoids better overall.
\end{Verbatim}
\end{assistantbox}

\begin{userbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Not only plots.
Every output which was produced when the full project ran.

Also explicitely tell me in details about all the baseline comparison
\end{Verbatim}
\end{userbox}

\begin{assistantbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Perfect request. I checked the latest **full `main.py` run output log** and all generated artifacts.

## Latest full run: what it produced (everything)

From the latest successful full run:
- **Exit status:** success (`exit_code: 0`)
- **Runtime:** ~9,772,093 ms (~2h 42m 52s)
- **Terminal outputs produced:**
  - Per-seed algorithm run outputs
  - Per-seed comparison summaries
  - Multi-seed statistics + paired t-tests
  - Scaling experiment logs
  - Energy-model sensitivity logs
  - Scenario-diversity logs
  - Final last-seed detailed summary
  - Mechanism analysis section (“why EA works”)
  - Bangladesh grid-intensity sensitivity section
  - Final completion banner

### Files produced/updated by this full run
- `results/simulation_results.json`
- `results/multiseed_summary.json`
- `results/energy_comparison.png`
- `results/cumulative_co2.png`
- `results/bar_comparison.png`
- `results/bar_co2_comparison.png`
- `results/energy_per_vehicle_cdf.png`
- `results/tx_power_distribution.png`
- `results/bs_load_distribution.png`
- `results/sinr_histogram.png`
- `results/network_topology.png`
- `results/scaling_energy_saving_vs_vehicles.png`
- `results/scaling_results.json`
- `results/energy_model_sensitivity.png`
- `results/energy_model_sensitivity.json`
- `results/energy_model_justification.md`
- `results/scenario_diversity_energy_saving.png`
- `results/scenario_diversity_results.json`

---

## Full baseline comparison (explicit + detailed)

I’m giving both:
1) **Multi-seed baseline comparisons** (most reliable headline), and  
2) **Last-seed detailed snapshot** (seed `11235`) for concrete numbers.

## 1) Multi-seed baseline comparison (from run log)

Energy-Aware (EA) vs each baseline in avg EPB:

- vs `rssi`: **+15.26% +- 1.07%**
- vs `sinr`: **+11.03% +- 1.21%**
- vs `load_aware_rssi`: **+15.42% +- 1.15%**
- vs `naive_nearest`: **+2.70% +- 1.32%**
- vs `literature_ul_ho`: **+15.31% +- 1.07%**
- vs `lb_aware_rsrp`: **+15.21% +- 1.24%**
- vs `mdpi_energy_efficient`: **+35.32% +- 6.68%**

Other multi-seed baseline context:
- EA total energy mean: **21280.15 J**
- RSSI total energy mean: **23409.17 J**
- EA outage mean: **16.37%** vs RSSI **22.75%**
- EA avg throughput: **24.265 Mbps** vs RSSI **22.616 Mbps**
- EA service availability: **83.64%** vs RSSI **77.25%**
- EA ping-pong rate: **20.46%** vs RSSI **34.54%**
- Paired tests (EA better than RSSI): highly significant (`p ~ 1e-18`, `1e-17`)

---

## 2) Last-seed detailed baseline comparison (seed 11235)

Reference EA metrics:
- Energy: **21162.94 J**
- EPB: **3.605e-08 J/bit**
- Handoffs: **2246**
- Throughput: **24.459 Mbps** (P5: **23.118 Mbps**)
- Outage: **16.64%**
- Availability: **83.36%**
- CO2: **0.002939 kg**

### EA vs `rssi`
- EPB saving: **16.05%**
- Total-energy saving: **9.04%**
- Handoffs reduced: **19.44%** (2246 vs 2788)
- Throughput higher: 24.459 vs 22.573 Mbps
- Outage lower: 16.64% vs 23.49%
- Availability higher: 83.36% vs 76.51%
- CO2 lower: 0.002939 vs 0.003231 kg

### EA vs `sinr`
- EPB saving: **12.81%**
- Total-energy saving: ~**7.02%**
- Same handoff count as RSSI baseline had in this run (EA still lower)
- Better throughput/outage/availability than SINR baseline.

### EA vs `load_aware_rssi`
- EPB saving: **16.32%**
- Total-energy saving: ~**9.14%**
- Handoffs: EA lower (2246 vs 2790)
- Throughput and outage both better for EA.

### EA vs `naive_nearest`
- EPB saving: **1.48%** (small but positive)
- **Important tradeoff:** naive has lower total Joules and much fewer handoffs (632), but EA still gives:
  - better throughput
  - lower outage
  - better availability
  - better EPB quality

### EA vs `literature_ul_ho`
- EPB saving: **16.32%**
- Throughput better, outage much better (16.64% vs 24.75%)
- But EA has more handoffs than this baseline (2246 vs 1872)

### EA vs `lb_aware_rsrp`
- EPB saving: **16.92%**
- Throughput/outage better for EA
- EA again has more handoffs than this baseline (2246 vs 1668)

### EA vs `mdpi_energy_efficient`
- EPB saving: **30.42%**
- MDPI shows very low total energy and very few handoffs (**28**) but with severe QoS collapse:
  - throughput only **8.293 Mbps**
  - outage **68.25%**
  - availability **31.75%**
- So EA is far better on service reliability while also better on EPB efficiency.

---

## Additional outputs present in `results/` (outside this specific main full-run block)

These also exist and are valid artifacts in your folder:
- `results/weather_sweep.json` + weather sweep plots
- `results/comprehensive_validation.json`
- `results/extrapolation_validation.png`
- `results/parameter_sweep.json`
- `results/pareto_frontier.png`

If you want, I can now give you a **single publishable table** (algorithm-by-algorithm, all key metrics, ranked) in the exact format for your paper/report.
\end{Verbatim}
\end{assistantbox}

\begin{userbox}
\begin{Verbatim}[breaklines=true,breakanywhere=true]
Okay Now check our this whole chatbox conversation.

Just convert this whole chat into a very beautiful and cool latex file.

NO TEXT ALTERATION FROM THE CHAT.
Just convert the full chat into a very detailed and brief and good looking latex file.
\end{Verbatim}
\end{userbox}

\end{document}
